A Switching Planner for Combined Task and Observation Planning

### 2011-02-09 subarchitectures/planner.sa/trunk/src/latex/AAAI11/switching.tex
small footnote

\noindent Each assumption corresponds to one distinct {\em
relaxed} visitation of the root term. Here, a conjunctive term is visited
iff its atomic subterms are visited, and zero or one of its immediate
probabilistic subterms are visited. For a sequential session, the
starting state corresponds to an assumption (usually unique) with
probability $1$. In our example, that starting state is:

>>>>

\noindent Each assumption corresponds to one distinct {\em
relaxed} visitation of the root term. Here, a conjunctive term is
visited iff its atomic subterms are visited, and zero or one of its
immediate probabilistic subterms are visited. For a sequential
session, the starting state corresponds to an assumption (usually
unique) with probability $1$.\footnote{To simplify the discussion, we
suppose that the root term of $(\pp{:init})$ lists all atoms that are
necessarily true.} In our example, that starting state is:
